\textbf{Emergency Service Location Optimization in a Multi-Zone District based on Population Distribution}

### 2013-11-16 LaTeX/paper.tex
Added equations

\usepackage{url}
\usepackage{caption}
% \usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
\graphicspath{{./Pictures/}}

\pagestyle{fancy}
\lhead{Team 4552}
\chead{Problem A}
\rhead{\thepage}

\renewcommand{\headrulewidth}{.8pt}
%\renewcommand{\footrulewidth}{.8pt}

@@

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$
In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$
The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$
The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, have a total average travel time of $T_A$.
$$T_A = \frac{T_{A+} + T_{A-}}{2}$$
We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$.
$$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$

@@

\subsection{The $n$ Ambulance Problem}

\subsubsection{$n=3$ Problem}

\subsubsection{$n=2$ Problem}

\subsubsection{$n=1$ Problem}

\subsection{Localized Single Zone Disaster}
In a localized catastrophic event such as those that happened on September 11, 2001, there will be
many casualties in a single location that require aid. Ambulances, and other emergency vehicles,
such as police cars and fire trucks, will need to respond quickly in order to aid the most critically
injured first, who will be sorted by triage. Therefore, it is very important for ambulances to be able to
reach the emergency as quickly as possible, regardless of the initial location of the ambulances and the
location of the emergency.

>>>>

\usepackage{url}
\usepackage{caption}
\usepackage{fullpage}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage{float}
\restylefloat{table}
\restylefloat{figure}
\usepackage{setspace}
\graphicspath{{./Pictures/}}

% \pagestyle{fancy}
% \lhead{Team 4552}
% \chead{Problem A}
% \rhead{}

% \renewcommand{\headrulewidth}{0.8pt}
% \renewcommand{\footrulewidth}{0.8pt}

@@

The function for zone-to-zone coverage in respect to travel time can be written out as 
$$Z_{AB}(t) = P_B \int^v_{T_{AB} - \frac{b}{2}} B(t) dt$$

In order to find the width of zone B, b, we can take the probability curve of differences in travel time within B, $F_B(s)$, and find the average travel time within B. This is the average difference in travel time, and is equal to $T_{B+}$. 
$$T_{B+} = \int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} s F_B(s) ds$$

The probability curve of differences in travel time within B, $F_B(s)$, can be found by performing a cross-correlation of $B(t)$ on itself, with $s$ being the difference in travel time plotted against frequency.
$$P_B(s) =\int^{T_{AB} + \frac{b}{2}}_{T_{AB} - \frac{b}{2}} B(t) * B(t-s) dt$$

The average travel time in the direction of A to B inside of A, $T_{A-}$, and the average travel time in the direction of B to A inside of A, $T_{A+}$, have a total average travel time of $T_A$. We can also write the ratio of $T_{A+}$ and $T_{A-}$, which is equivalent to the ratio of $T_{BA}$ and $T_{AB}$. The same can be done with $T_{B}$.
$$T_A = \frac{T_{A+} + T_{A-}}{2}$$
$$\frac{T_{A+}}{T_{A-}} = \frac{T_{BA}}{T_{AB}}$$ 
$$\frac{T_{B+}}{T_{B-}} = \frac{T_{AB}}{T_{BA}}$$

This allows us to solve for $T_{A-}$  and $T_{B+}$.
$$T_{A-} = \frac {2T_A}{1+ \frac{T_{BA}}{T_{AB}}}$$
$$T_{B+} = \frac {2T_B}{1+ \frac{T_{AB}}{T_{BA}}}$$

@@

\subsection{3 Ambulance Cover}

\subsection{2 Ambulance Cover}

\subsection{1 Ambulance Cover}

\subsection{Catastrophic Cover}
In a localized catastrophic event such as those that happened on September 11, 2001, there will be
many casualties in a single location that require aid. Ambulances, and other emergency vehicles,
such as police cars and fire trucks, will need to respond quickly in order to aid the most critically
injured first, who will be sorted by triage. Therefore, it is very important for ambulances to be able to
reach the emergency as quickly as possible, regardless of the initial location of the ambulances and the
location of the emergency.
